Hydrodynamics of two vesicles interacting via a Van der Waals potential

### 2018-12-18 vesicle_code/docs/adhesion/adhesion.tex
adding new figure

Here we investigate rheology of suspensions by computing the effective
viscosity. The effective viscosity is defined as the viscosity of a
homogeneous Newtonian fluid with the same energy dissipation per
macroscopic element of fluid.  In a simple shear flow, the ambient
velocity field is given by $\uu(\xx) = (\chi y,0)$, where $\chi$ is the
shear rate.  In dilute suspensions, the interaction between vesicles can
be ignored, and the intrinsic viscosity is
\begin{align*}
  [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
  \frac{1}{\chi \mu_0 T} \int_{T_i}^{T_e} 
  \langle \sigma_{12} \rangle dt,
\end{align*}
where
\begin{align*}
  \langle \sigma \rangle = \frac{1}{|\omega|} \int_{\gamma}
    \xxi \otimes \xx ds.
\end{align*}
Here, $[\mu]$ is the intrinsic viscosity, $|phi$ is the area fraction of
vesicles, $\sigma$ is the stress due to the vesicles, and $\langle \cdot
\rangle$ is the spatial average.  For dilute suspensions of rigid
bodies, the intrinsic viscosity was derived by Eienstein~\cite{}, and it
is given by
\begin{align*}
  something.
\end{align*}
For vesicles, the intrinsic viscosity was derived by Misbah~\cite{}, and
it is given by
\begin{align*}
  something.
\end{align*}

>>>>

Here we investigate rheology of suspensions by computing the effective
viscosity. The effective viscosity is defined as the viscosity of a
homogeneous Newtonian fluid with the same energy dissipation per
macroscopic element of fluid.  In a simple shear flow, the ambient
velocity field is given by $\uu(\xx) = (\chi y,0)$, where $\chi$ is the
shear rate.  In dilute suspensions, the interaction between vesicles can
be ignored, and the intrinsic viscosity is
\begin{align*}
  [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
  \frac{1}{\chi \mu_0 T} \int_{T_i}^{T_e} 
  \langle \sigma_{12} \rangle dt,
\end{align*}
where
\begin{align*}
  \langle \sigma \rangle = \frac{1}{|\omega|} \int_{\gamma}
    \xxi \otimes \xx ds.
\end{align*}
Here, $[\mu]$ is the intrinsic viscosity, $|phi$ is the area fraction of
vesicles, $\sigma$ is the stress due to the vesicles, and $\langle \cdot
\rangle$ is the spatial average.  For dilute suspensions of rigid
bodies, the intrinsic viscosity was derived by Eienstein~\cite{}, and it
is given by
\begin{align*}
  something.
\end{align*}
For vesicles, the intrinsic viscosity was derived by Misbah~\cite{}, and
it is given by
\begin{align*}
  something.
\end{align*}
\begin{figure}[htp]
  \includegraphics[scale=1]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
  \caption{\label{fig:shearIntrinsicViscosity} The intrinsic viscosity
  of a tank treading vesicle (blue) and a doublet (red).  The shear rate
is $\chi = 0.5$, the Hamaker constant is $\sigma = 0.7$, and the
adhesion length scale is $\delta = 0.4$.  The length of the vesicles at
each of the reduced areas is fixed, while the area changes with
differing reduced areas.}
\end{figure}
